\bf Fast and Efficient Black Box Optimization using the Parameter-less Population Pyramid

### 2014-10-10 Fast and Efficient Black Box Optimization using the Parameter-less Population Pyramid/main.tex
Last commit before sending to Bill

\subsection{Deceptive Step Trap}
The number of solutions stored at the fourth level of Deceptive Step Trap is
significantly lower than that of the third or fifth levels, breaking the decreasing
trend of the other six problems. Figure~\ref{fig-level-success} has a similar
aberration, with crossover success dropping to  0.0004\% before rebounding and
following the more common trajectory. This behavior exists in all other problem
sizes tested, with the dips occurring at exactly the same level.

>>>>

\subsubsection{Deceptive Step Trap}
The number of solutions stored at the fourth level of Deceptive Step Trap is
significantly lower than that of the third or fifth levels, breaking the decreasing
trend of the other six problems. Figure~\ref{fig-level-success} has a similar
aberration, with crossover success dropping to  0.0004\% before rebounding and
following the more common trajectory. This behavior exists in all other problem
sizes tested, with the dips occurring at exactly the same level.
